\texttt{MSnbase}, efficient R-based access and manipulation of raw mass spectrometry data

### 2020-04-27 msnbase2.Rnw
add boxcar code, finish section

<<filter, eval = FALSE, echo = TRUE>>=
x <- x_dsk %>%
    filterRt(c(1000, 3000)) %>%
    filterMz(120, 135)
x[precursorIntensity(x) > 11e6, ]
@

@@

The \texttt{MSnExp} data structure and its interface constitute a
efficient prototyping environment for computational method
development. We illustrate this by demonstrating how to implement the
BoxCar\cite{Meier:2018} acquisition method. In a nutshell, BoxCar
acquisition aims at improving the detection of intact precursor ions
by distributing the charge capacity over multiple narrow m/z segments
and thus limiting the proportion of highly abundant precursors in each
segment. A full scan is reconstructed by combining the respective
adjacent segments of the BoxCar acquisitions. The
\texttt{MSnbaseBoxCar} package\cite{MSnbaseBoxCar} is a small package
that demonstrates this. The simple method is composed of three steps:

@@

\item Identify and filter the groups of spectra that represent
  adjacent BoxCar acquisitions (Figure~\ref{fig:bc}~(b)). This can be
  done using the `filterString` metadata variable (see code chunk
  above) that identifies BoxCar spectra by their adjacent M/Z segments
  with the \texttt{bc\_groups()} function from \texttt{MSnbaseBoxCar}.

@@

@@

@@

Examples: 3D MSmap, boxcar, centroiding vignette

>>>>

<<filter, eval = FALSE, echo = TRUE>>=
ms <- ms %>%
    filterRt(c(1000, 3000)) %>%
    filterMz(120, 135)
ms[precursorIntensity(ms) > 11e6, ]
@

@@

The \texttt{MSnExp} data structure and its interface constitute a
efficient prototyping environment for computational method
development. We illustrate this by demonstrating how to implement the
BoxCar\cite{Meier:2018} acquisition method. In a nutshell, BoxCar
acquisition aims at improving the detection of intact precursor ions
by distributing the charge capacity over multiple narrow m/z segments
and thus limiting the proportion of highly abundant precursors in each
segment. A full scan is reconstructed by combining the respective
adjacent segments of the BoxCar acquisitions. The
\texttt{MSnbaseBoxCar} package\cite{MSnbaseBoxCar} is a small package
that demonstrates this. The simple method is composed of three steps
is described below and illustrated with code from
\texttt{MSnbaseBoxCar} in the following code chunk.

@@

\item Identify and filter the groups of spectra that represent
  adjacent BoxCar acquisitions (Figure~\ref{fig:bc}~(b)).. This can be
  done using the `filterString` metadata variable that identifies
  BoxCar spectra by their adjacent M/Z segments with the
  \texttt{bc\_groups()} function and filtering relevant spectra with
  the \texttt{filterBoxCar()}.

@@

<<bc1, echo=TRUE, eval=FALSE>>=
raw_bc %>% 
    bc_groups() %>%       ## identify BoxCar groups (bc_groups)
    filterBoxCar() %>%    ## keep only BoxCar spectra
    bc_zero_out_box() %>% ## remove signal outside of BoxCar segments
    combineSpectra(fcol = "bc_groups", ## reconstruct full spectrum
                   method = boxcarCompbine)
@

@@

All the functions for the processing of BoxCar spectra and segments in
\texttt{MSnbaseBoxCar} were developed using existing functionality
implemented in \texttt{MSnbase}, illustrating the flexibility and
adaptability of the \texttt{MSnbase} package for computational mass
spectrometry method development.

@@

The R environment is well known for the quality of its visualiation
capacity. This also holds true for mass
spectrometry\cite{Gatto:2015,protViz}.

### 2020-04-27 msnbase2.tex
add boxcar code, finish section

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{x} \hlkwb{<-} \hlstd{x_dsk} \hlopt{%>%}
    \hlkwd{filterRt}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{1000}\hlstd{,} \hlnum{3000}\hlstd{))} \hlopt{%>%}
    \hlkwd{filterMz}\hlstd{(}\hlnum{120}\hlstd{,} \hlnum{135}\hlstd{)}
\hlstd{x[}\hlkwd{precursorIntensity}\hlstd{(x)} \hlopt{>} \hlnum{11e6}\hlstd{, ]}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

@@

Examples: 3D MSmap, boxcar, centroiding vignette

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{ms} \hlkwb{<-} \hlstd{ms} \hlopt{%>%}
    \hlkwd{filterRt}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{1000}\hlstd{,} \hlnum{3000}\hlstd{))} \hlopt{%>%}
    \hlkwd{filterMz}\hlstd{(}\hlnum{120}\hlstd{,} \hlnum{135}\hlstd{)}
\hlstd{ms[}\hlkwd{precursorIntensity}\hlstd{(ms)} \hlopt{>} \hlnum{11e6}\hlstd{, ]}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{raw_bc} \hlopt{%>%}
    \hlkwd{bc_groups}\hlstd{()} \hlopt{%>%}       \hlcom{## identify BoxCar groups (bc_groups)}
    \hlkwd{filterBoxCar}\hlstd{()} \hlopt{%>%}    \hlcom{## keep only BoxCar spectra}
    \hlkwd{bc_zero_out_box}\hlstd{()} \hlopt{%>%} \hlcom{## remove signal outside of BoxCar segments}
    \hlkwd{combineSpectra}\hlstd{(}\hlkwc{fcol} \hlstd{=} \hlstr{"bc_groups"}\hlstd{,} \hlcom{## reconstruct full spectrum}
                   \hlkwc{method} \hlstd{= boxcarCompbine)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

The R environment is well known for the quality of its visualiation
capacity. This also holds true for mass spectrometry
data~\cite{Gatto:2015,protViz}.
